### 2017-06-10 paper.tex
Minor edits

By definition,
many open education projects satisfy the first criterion,
but very few satisfy the second:
while their lessons might occasionally be updated by a small author group,
as happens when a new edition of a book is edited and published,
this is not the same as continuous improvement by a large community of contributors.
The ten simple rules that follow summarize what we have learned about doing that
as maintainers, editors, and reviewers of lessons used by tens of thousands of people.

@@

Another example is Software Carpentry's instructor training program.
First offered in 2012,
is now a two-day course delivered both in-person and online
\cite{lessons-learned,instructor-training,how-to-teach-programming}.
Not only does it teach good pedagogical practices,
it serves and an onboarding process to get everyone on the same page
regarding who lessons are for,
how they are delivered,
and how they are maintained.

@@

It takes a village to ensure
the steady improvement and adaptation that will give a lesson a long life.
Ensuring this, however, is not straightforward.

Making the process explicit is key.
New contributors require a straightforward and transparent introduction
to understand the process of tweaking and adapting lessons.
Licensing, code of conduct, governance, and contribution procedure
all need to be explicit rather than implicit
to lower the social barriers to contribution.

Tools can help,
especially if they allow proposed changes to be viewed and discussed
prior to their incorporation/merger into the lessons
(in open source software development this is known as ``pre-merge review'').
Yet some of these tools come with a considerable up-front learning curve.
GitHub with pull requests is ideal for pre-merge review, for instance,
but it requires contributors to understand the basics of the git version control software.
Allowing people to edit a Google Doc or Wiki-based editing does not offer pre-merge review,
but the low barrier to entry can help get conversations started.
In a pinch,
work with contributors to find a comfort zone:
don't let a collaboration flounder on technological choice.
But make sure not to overwhelm either:
threaded discussion on paticular topics (e.g. GitHub issues) can help increase the signal-to-noise ratio
by reducing long reply-all email excahnges.

Ultimately,
community dynamics are more important than platform.
We have seen the 90/9/1 rule:
90\% of people watch, 9\% discuss, 1\% do.
This requires a gentle on-ramp for new contributors,
that we make it easy for people to submit errata and suggestions,
and that editors may need to do triage to ensure that voices are heard.
Finally, with so many voices and contributions come caution.
Working in the open can be great,
but can also unintentionally suppress voices.
At Programming Historian,
for example,
an ombudsperson is available for private chats and facilitation.

@@

If lessons are being released regularly,
it is worth automating this release process
with a simple shell script.
Old versions of lessons should be archived in a discoverable location for reference.

>>>>

Open education projects satisfy the first criterion by definition,
but very few projects satisfy the second.
While their lessons might occasionally be updated by a small author group,
as happens when a new edition of a book is edited and published,
this is not the same as continuous improvement by a large community of contributors.
The ten simple rules that follow summarize what we have learned about doing that
as maintainers, editors, and reviewers of lessons used by tens of thousands of people.

%%%%% Figure  dissociation 
\begin{figure}[ht]  % h = here, t = top, b = bottom, p = float
\includegraphics[width=\linewidth]{figure1}
\caption{Graphical abstract of 10 simple rules for collaborative lesson development}
\label{figure1}
\end{figure}
%

@@

An example of how to teach these practices is Software Carpentry's instructor training program.
First offered in 2012,
is now a two-day course delivered both in-person and online
\cite{lessons-learned,instructor-training,how-to-teach-programming}.
Not only does it teach good pedagogical practices,
it serves and an onboarding process to get everyone on the same page
regarding who lessons are for,
how they are delivered,
and how they are maintained.

@@

Making the process for contributing to a lesson explicit is
the key to actually getting contributions.
New contributors require a straightforward and transparent introduction
to understand the process of tweaking and adapting lessons.
Licensing, code of conduct, governance, and contribution procedure
all need to be explicit rather than implicit
to lower the social barriers to contribution.

Tools can help,
especially if they allow proposed changes to be viewed and discussed
prior to their incorporation/merger into the lessons
(in open source software development this is known as ``pre-merge review'').
Providing a gentle on-ramp for new contributors is essential,
but some tools come with a considerable up-front learning curve.
GitHub with pull requests is ideal for pre-merge review, for instance,
but it requires contributors to know how to use Git,
which is a famously user-hostile tool.
Allowing people to edit a Google Doc or Wiki-based editing does not offer pre-merge review,
but the low barrier to entry can help get conversations started.

The best way to choose tools for managing lessons
is to look for those that provide a gentle on-ramp for new contributors.
Ask potential contributors what they are comfortable with
rather than requiring \emph{them} to come to \emph{you}.
Remember also that contributing to a lesson is probably not their top priority,
and look for ways to reduce their cognitive load.
For example,
threaded discussion on particular topics (e.g., using GitHub issues)
can help increase the signal-to-noise ratio
by reducing long reply-all email excahnges.

Finally,
working in the open can be great,
but can also unintentionally suppress voices.
At Programming Historian,
for example,
an ombudsperson is available for private chats and facilitation.

@@

If lessons are being released regularly,
automate the process
with a shell script or something similar.
Old versions of lessons should be archived in a discoverable location for reference.
